---
title: "Fraley et al. (2022) N-pact factor"
subtitle: "Assessment of computational reproducibility via refactoring of Fraley's code"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

# Install packages and import data

```{r}
library(pwr)
library(tidyverse)
library(janitor)
library(viridis)
library(knitr)
library(kableExtra)

```

# Data

Fraley's commented out code for data wrangling, below, was run once to create data_combined.csv. All future runs simply loaded data_combined.csv and ran analyses on it.

```{r}

# # Create something that combines data4 (JC) and data5 (AKG)
# #try relabel the cols of JC data4
# 
# # Analyses for N-Pact 2011-2019
# # Raw data are stored in two files. They'll be imported and merged here.
# 
# # Read data file from current directory
# 
# data5 = read.csv("../data/raw/dataAKG.csv", stringsAsFactors=FALSE)	# AKG phase
# data4 = read.csv("../data/raw/data4.csv", stringsAsFactors=FALSE)	# JC phase
#
# data3 = data4[,c("Index", "Random", "PDF", "PDF","Social","JPSP_Section",
#                  "Journal","Year","Title","Journal","TotalStudiesA","N1A","Design","CommentsA",
#                  "CoderA","TotalStudiesB","N1B","Design","CommentsB","CoderB","coder_dif","coder_disagree","ChrisResolve","CommentsChris",
#                  "Design","N","Design")]
# 
# 
# colnames(data3) = c("Index",          "Random" ,        "Target_PDF",     "PDF",            "Social_PS",     
#                     "JPSP_Section",   "Journal",        "Year",           "Title",          "Journal_full",  
#                     "num_studiesa",   "na",             "DA",             "commentsa",      "codera",        
#                     "num_studiesb",   "nb",             "DB",             "commentsb",      "coderb" ,       
#                     "coder_dif",      "coder_disagree", "ChrisResolve",   "ChrisNotes",     "ChrisD",        
#                     "N" ,             "D"   )
# 
# 
# data6 = rbind(data3, data5)
# 
# dim(data6)
# 
#
#
#
# data_combined <- data6
#
# #to simplify things, replace "" with NA for data_combined$D
#
# data_combined$D[which(data_combined$D=="")]=NA
# 
# data_combined <- data_combined |>
#   mutate(Journal = ifelse(Journal == "PS", "PS:S", Journal))
#
# write_csv(data_combined, "../data/processed/data_combined.csv")
data_combined <- read_csv("../data/processed/data_combined.csv")

```

# Descriptives

How many articles were coded? 

```{r}

data_combined |>
  filter(!is.na(N)) |>
  distinct(Title) |>
  count(name = "k articles") |>
  kable() |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

How many studies were coded? 

```{r}

data_combined |>
  filter(!is.na(N)) |>
  count(name = "k studies") |>
  kable() |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
  
```

How many studies for each design type? 

b = between, m = mixed, w = within.

```{r}

data_combined |>
  filter(!is.na(N)) |>
  distinct(Title, D) |>
  count(D) |>
  mutate(percent = janitor::round_half_up(n/sum(n), 2)) |>
  kable() |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Table 1 N-Pact Factors 

Using between-persons designs only.

```{r}

# filter to include only between ("b") group designs ("D")
# Filter out non-social studies published in psych science
data_table_1_filtered <- data_combined |>
  filter(
    D == "b" & 
      ((Journal == "PS:S" & (Social_PS == 1 | is.na(Social_PS))) | Journal != "PS:S")
  )

# calculate median N for each Journal and Year
# round using typical half-up rule and not R's weird rounding
data_table_1_n_long <- data_table_1_filtered |>
  group_by(Journal, Year) |>
  summarize(median_n = janitor::round_half_up(median(N, na.rm = TRUE), 0)) |>
  ungroup()

# Calculate median median n for each journal
data_table_1_n_aggregate <- data_table_1_n_long |>
  group_by(Journal) |>
  summarize(median_median_n = median(median_n, na.rm = TRUE)) |>
  ungroup()

# Calculate k studies used to calculate median ns
data_table_1_k_long <- data_table_1_filtered |>
  count(Journal, Year, name = "k_studies")

# combine Ns and Ks, reshape, and order Journal column by aggregate median median n 
data_table_1 <- 
  full_join(data_table_1_n_long, data_table_1_k_long, by = c("Journal", "Year")) |>
  mutate(result = paste0(median_n, " (", k_studies, ")")) |>
  select(-median_n, -k_studies) |>
  pivot_wider(names_from = Year, 
              values_from = result) |>
              #names_prefix = "NF ") |>
  left_join(data_table_1_n_aggregate, by = "Journal") |>
  mutate(Journal = fct_reorder(Journal, median_median_n)) |>
  arrange(desc(Journal))

# print table
data_table_1 |>
  select(Journal, 
         Aggregate = median_median_n, 
         starts_with("20")) |>
         #starts_with("NF")) |>
  kable() |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Table 2 Estimated Statistical Power 

to Detect an Average Published Effect Size ($\rho$ = .20)

Using between-persons designs only.

```{r}

# use median n to calculate power
data_table_2_long <- data_table_1_n_long |>
  mutate(power = janitor::round_half_up(pwr.r.test(r = .2, sig.level = 0.05, n = median_n)$power*100, 0)) |>
  select(-median_n)

# reshape table, order Journal column by that used in previous table
data_table_2 <- data_table_2_long |>
  pivot_wider(names_from = Year, 
              values_from = power) |>
              #names_prefix = "power ") |>
  mutate(Journal = fct_relevel(Journal, levels(data_table_1$Journal))) |>
  arrange(desc(Journal))

# print table
data_table_2 |>
  kable() |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Table 3 Estimated False-Discovery Rates 

Assuming No p-Hacking or Questionable Research Practices

Using between-persons designs only, and various assumptions about the P(null = TRUE)

```{r}

# select a subset power data from first and last year studied, reshape 
data_power_subset <- data_table_2 |>
  select(Journal, `2011`, `2019`) |>
  pivot_longer(cols = c(`2011`, `2019`), 
               names_to = "Year",
               values_to = "power") 

# duplicate data with different values of $P(H_0)$,
# calculate False Discovery Rate
data_table_3 <- bind_rows(
  mutate(data_power_subset, baserate_null = .50),
  mutate(data_power_subset, baserate_null = .80)
) |>
  mutate(power = power/100,
         fdr = janitor::round_half_up( (baserate_null*.05) / (  (baserate_null*.05) + ((1-baserate_null)*power)  ), 2)) |>
  select(Journal, Year, baserate_null, fdr) |>
  pivot_wider(names_from = c(Year, baserate_null),
              values_from = fdr)

# print table
data_table_3 |>
  kable(col.names = c("Journal", "$P(H_0)$ = 0.5", "$P(H_0)$ = 0.8", "$P(H_0)$ = 0.5", "$P(H_0)$ = 0.8"),
        escape = FALSE) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
  add_header_above(c(" " = 1, "2011" = 2, "2019" = 2))

```

# Figure 1 Illustration of how false-discovery rates vary as a function of statistical power.

(made in a program other than R, I think)

# Figure 2 Change in N-pact over time

Not limited to between-only designs

```{r}

# Filter out non-social studies published in psych science
# unlike Table 1, do NOT filter group designs ("D")
# calculate median Ns
# order Journal column by same used in Table 1
data_figure_2 <- data_combined |>
  filter(
    ((Journal == "PS:S" & (Social_PS == 1 | is.na(Social_PS))) | Journal != "PS:S")
  ) |>
  group_by(Journal, Year) |>
  summarize(median_n = janitor::round_half_up(median(N, na.rm = TRUE), 0)) |>
  ungroup() |>
  mutate(Journal = fct_rev(fct_relevel(Journal, levels(data_table_1$Journal))))

# plot 
ggplot(data_figure_2, aes(as.factor(Year), median_n, color = Journal, group = Journal)) +
  geom_line() +
  geom_point() +
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9) +
  theme_classic() +
  ylab("Median N") +
  xlab("Year")

```

# Figure 3 Estimated statistical power to detect a population association ($\rho$) of .20 over time

```{r}

# order Journal column by same used in Table 1, then plot
data_table_2_long |>
  mutate(Journal = fct_rev(fct_relevel(Journal, levels(data_table_1$Journal)))) |>
  ggplot(aes(as.factor(Year), power/100, color = Journal, group = Journal)) +
  geom_hline(yintercept = .80, linetype = "dotted") +
  geom_line() +
  geom_point() +
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9) +
  theme_classic() +
  ylab("Power") +
  xlab("Year")

```


